---
title: "Survey data visulization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Workflow

This is a workflow of analyzing survey data from Qualtrics. When exporting data from Qualtrics, make sure to select "Use choice text" and "Split multi-value fields into columns" and export the data as csv file. 

After downloading the file, open it and delete the first **two rows** of the raw data. Now you should have the spreadsheet with only one row as its head. This will give convenience to further data wrangling in R. 

## Import useful libraries and read the raw data to R

```{r}
library(tidyverse)
library(ggplot2)
raw<-read_csv("rawdata2.csv")
names(raw)<-str_replace_all(names(raw), c("#" = "."))
colnames(raw)[5]<-"Duration"
colnames(raw)[9]<-"Distribution"
raw$StartDate<-as.Date(raw$StartDate,format='%m/%d/%y')
```

## Filter the valid sample by progress, distribution, duration and startdate
```{r}
raw<-raw[raw$StartDate>"2020-11-23",]
raw<-raw[raw$Progress>70 & raw$Duration>180 & raw$Distribution != "preview",]

```

